%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[11pt,a4paper,roman]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{orange} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Kayli} % Your first name
\familyname{Kallina} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{1650 West 6th Street Apt M}{Austin, Texas 78703}
\mobile{(979) 758 2010}
\email{kaylikallina@utexas.edu}
% The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example


%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2018-present}{Dell Medical School}{}{University of Texas at Austin}{}{M.D., anticipated May 2022}
\cventry{2010--2014}{B.S. in  Psychology}{}{University of Texas at Austin}{}{Education Minor}
% Arguments not required can be left empty


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Employment}

\cventry{2017 - 2018}{Emergency Department Scribe}{\textsc{PhysAssist Scribes}}{Dearborn, MI}{}{}

\cvlistitem{Awarded Northeast Region Scribe of the Month for April 2018}

%------------------------------------------------

\cventry{2015--2017}{Research Technician}{\textsc{Colgin Lab}}{University of Texas}{}{I designed and built devices for in vivo electrophysiological experiments in freely behaving animal models, prepared histological samples, and performed state-of-the-art microscopy techniques. I supervised research assistants at the undergraduate and postbac level, and trained graduate students, postdoctoral researchers, and visiting scholars in electrophysiological recording device construction. I was also responsible for maintaining a safe laboratory environment.
\newline{}\newline{}
Detailed achievements:
\begin{itemize}
\item Provided recording devices used to collect data that led to four publications
\item Developed a comprehensive instructional manual on the assembly of recording devices that has been adopted by labs in the US, Taiwan, and India
\item Modified and implemented a new device design that increased the number of simultaneous recordings collected per animal
\item Led small group session on neuron rate coding for Dell Medical School Health Sciences Summer Camp 2016
\item Obtained Green Lab certification for implementing sustainable laboratory practices, and served as first Green Labs Ambassador for the Colgin Lab
\end{itemize}}

%------------------------------------------------

\cventry{Fall 2013}{English Teacher}{\textsc{Coprodeli}}{Callao, Per\'u}{}{I prepared and taught English lessons to a hundred elementary students daily, and to faculty twice a week.
\newline{}\newline{}
Detailed achievements:
\begin{itemize}
\item Organized first English spelling competition and lunchtime karaoke
\item Collaborated with board of directors to evaluate success of bilingual program
\end{itemize}}

%------------------------------------------------
\pagebreak
\cventry{Summer 2011 \& 2012}{Lifeguard}{\textsc{El Campo Aquatic Center}}{El Campo, TX}{}{}

%------------------------------------------------

\cventry{Summer 2010 \& 2011}{Dispatching/Operations Technician}{\textsc{Kallina Dryer Inc.}}{Altair, TX}{}{During harvest, I weighed freight trucks using an industrial scale, analyzed rice samples, and operated conveyors to direct grain to treatment and storage facilities.}

%------------------------------------------------




%----------------------------------------------------------------------------------------
%	RESEARCH SECTION
%----------------------------------------------------------------------------------------

\section{Research}


%------------------------------------------------

\cventry{2013--2014}{Undergraduate Assistant}{\textsc{Cog. Neuro. Lab}}{University of Texas}{}{For an average of 10 hours per week, I conducted behavioral and neuropsychological tests. I processed blood specimen for further analysis, and was certified as a Level 1 MRI Operator.}

%------------------------------------------------

%----------------------------------------------------------------------------------------
%	HEALTHCARE SECTION
%----------------------------------------------------------------------------------------

\section{Healthcare}

%------------------------------------------------

\cventry{Spring 2017}{Volunteer}{\textsc{C.D. Doyle Clinic}}{Austin, TX}{\textit{Seven hours}}{I participated in a student-run clinic to offer free medical services to underserved residents of Austin}

\cventry{Summer 2017}{Physician shadowing}{\textsc{Rice Medical Center}}{Eagle Lake, TX}{}{I observed primary care consultations in a Rural Family Medicine clinic. I also attended rounds and outpatient wound care services at the center's Critical Access Hospital.}

\cvlistitem{R. Russell Thomas, Jr., DO, Family Medicine, \textit{Fifty hours}}

\cvlistitem{Alyssa Molina, MD, Family Medicine, \textit{Twenty hours}}

%------------------------------------------------

\cventry{Fall 2014}{Occupational Therapy shadowing}{\textsc{Mentis Neuro}}{Dripping Springs, TX}{}{I observed individual and group therapy for inpatients recovering from Traumatic Brain Injury.}

\cvlistitem{Roxane Nichols, OTR, \textit{Twenty hours}}

%------------------------------------------------


%------------------------------------------------

%----------------------------------------------------------------------------------------
%	COMMUNITY SERVICE SECTION
%----------------------------------------------------------------------------------------

\section{Community Service}

\cventry{Spring 2017}{Trainee}{\textsc{Spanish Community Interpreter Project}}{Washtenaw County, MI}{\textit{Thirty hours}}{}
\cventry{2017}{Advocate}{\textsc{Partners in Care Concierge}}{Ann Arbor, MI}{\textit{Twenty hours}}{Accompany English and/or Spanish-speaking elderly patients to medical appointments.}

%------------------------------------------------

\cventry{Spring 2016}{Teaching Assistant}{\textsc{Adults with IDD}}{University of Texas}{\textit{Twenty hours}}{}
\cvlistitem{Facilitated a supportive and inclusive learning environment for adults with intellectual and developmental disabilities.}
\cvlistitem{Oversaw the safe arrival and departure of students to weekly, evening classes.}

%------------------------------------------------

\cventry{2014--2015}{English Teacher}{\textsc{Casa Marianella}}{Austin, TX}{\textit{Two hundred hours}}{}
\cvlistitem{Completed Literacy Coalition of Central Texas English Forward training.}
\cvlistitem{Created English curriculum for immigrant and refugee adult learners}
\cvlistitem{Led evening classes and coordinated Show and Tell events}
\cvlistitem{Prepared dinner for forty residents of the emergency shelter}
\cvlistitem{Provided career building support for shelter residents}
\cvlistitem{Developed cultural competency by communicating effectively with a diverse, international population.
}

%------------------------------------------------

\cventry{Spring 2014}{Reading Tutor}{\textsc{Linder Elementary}}{Austin, TX}{\textit{Ten hours}}{}

%------------------------------------------------

\cventry{2011--2012}{HOSTS Reading Mentor}{\textsc{Metz Elementary}}{Austin, TX}{\textit{Fifty hours}}{}

%------------------------------------------------

\cventry{Spring 2011}{Classroom Assistant}{\textsc{Reagan High School}}{Austin, TX}{\textit{Forty hours}}{}

%------------------------------------------------

\cventry{Dec. 2010}{Music Therapy}{\textsc{Columbus Elementary}}{Columbus, TX}{\textit{Fourteen hours}}{}

%------------------------------------------------

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}

\cvitem{2015}{Best "Unchalk Talk" at UT Institute for Neuroscience retreat}
\cvitem{2012--2014}{University of Texas Service Scholar}
\cvitem{2010--2014}{Terry Foundation Scholar}
\cvitem{2010--2014}{Wintermann Foundation Scholar}
\cvitem{2010--2014}{Star of Texas Fair \& Rodeo Scholar}
\cvitem{2010}{Valedictorian of Rice CISD High School}

%----------------------------------------------------------------------------------------
%	EXTRACURRICULAR SECTION
%----------------------------------------------------------------------------------------

\section{Extracurricular Activities}

\cventry{2011--2014}{AIESEC}{\textsc{Austin, TX}}{}{}{AIESEC is a student-run international organization that matches university students to internships abroad.}

\cvlistitem{Interviewed, matched, and arranged J-1 visa documents for incoming Austin interns.}
\cvlistitem{Most Valuable Member of Talent Management branch (Fall 2012).}
\cvlistitem{Established membership satisfaction survery.}
\cvlistitem{Planned two formal banquets for fifty members and guests.}
\cvlistitem{Coordinated first multicultural fair, booked local musicians, and hosted a certified Green Event.}

\cventry{2011--2014}{University of Texas Service Scholars}{\textsc{Austin, TX}}{}{}{In this program at the Lyndon B. Johnson School of Public Affairs, I completed fifty hours of volunteer work in the education sector each semester. I attended biweekly seminars on leadership and public service, where I presented my work to fellow scholars and program coordinators.}

%----------------------------------------------------------------------------------------
%	MISCELLANEOUS SECTION
%----------------------------------------------------------------------------------------

\section{Miscellaneous}

\cventry{Summer 2012}{Study Abroad}{\textsc{Antigua, Guatemala}}{}{}{I explored sociocultural influences on learning. I also prepared and conducted weekly English language lessons for twenty-seven elementary age Spanish speakers.}

\cventry{}{Computer Skills}{}{}{}{}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistdoubleitem{Microsoft Office}{Google Drive}
\cvlistdoubleitem{R}{\LaTeX}

\cventry{}{Languages}{}{}{}{}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistdoubleitem{English (native)}{Spanish (fluent)}

\cventry{}{Hobbies}{}{}{}{}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistdoubleitem{Reading}{Guitar/Singing}
\cvlistdoubleitem{Trail Running}{Cooking}





\end{document}
